Four reasons your build is slow

### 2019-01-17 paper.tex
fix some reference errors

In the previous section we discussed zstd's build, which turned out to be unnecessarily sequential
because two single shell calls which compiled and linked many files at once could be broken up
into many parallel compilation jobs which could then be linked after.  These two commands could
have been written as follows in fig. \ref{code:cc5} and fig. \ref{code:cc6} respectively, instead of as they were
originally in fig. \ref{code:cc1} and fig. \ref{code:cc2} and would have resulted in the same
build performance, but would make it possible for our tool to detect that they are unnecessarily
sequential.

@@

  These recipes compiling individual files can run in parallel, as shown in the previous section,
  and our tool can detect this by using the build graph and the system call information gathered
  by strace and applying the methods described in section \ref{revisegraphs}.  When the span
  of the new graph is calculated it reflects the fact that these compilations can occur in
  parallel and is 8 seconds rather than the original 45 seconds; these times are longer than
  those mentioned in the previous section because strace inflates the running time of the
  commands it traces.

>>>>

In the previous section we discussed zstd's build, which turned out to be unnecessarily sequential
because two single shell calls which compiled and linked many files at once could be broken up
into many parallel compilation jobs which could then be linked after.  These two commands could
have been written as follows, respectively, instead of as they were
originally in fig. \ref{code:cc1} and fig. \ref{code:cc2}, and would have resulted in the same
build performance, but would make it possible for our tool to detect that they are unnecessarily
sequential.

@@

  These recipes compiling individual files can run in parallel, as shown in the previous section,
  and our tool can detect this by using the build graph and the system call information gathered
  by strace and applying the methods described in section \ref{sec:revisegraphs}.  When the span
  of the new graph is calculated it reflects the fact that these compilations can occur in
  parallel and is 8 seconds rather than the original 45 seconds; these times are longer than
  those mentioned in the previous section because strace inflates the running time of the
  commands it traces.
